The abundance of Bullet Groups in $\Lambda$CDM

### 2014-03-08 paper/ms.tex
Update ms.tex

The first region has $\mu\approx-1$ and $D_{\rm off}>0.6$, which
locates the systems where a head-on collision has just started. The
sub-halo is close to the boundary of the host halo and is
infalling. The second region has $\mu\approx 1$ and $D_{\rm off}<0.6$;
at this stage the collision continues after the first crossing of the
host's center, the low number of halos with radial infalling velocities
and displacements $D_{\rm off}>0.6$ sugesst that this the maximum
range of radii for the apogee.  The third region corresponds to
$\mu\approx-1$ and $D_{\rm off}<0.6$ which corresponds to the
secondary infall after apogee.

@@

These different collision geometries will produce different results in
terms of the displacement between dark matter and baryons. Strictly
speaking, the results we have derived so far, apply to multimodal groups and their
expected separation betwen the two dominant dark matter clumps but it
should not be interpreted that all have a corresponding DM-baryon
displacement. The systems where the halo is starting to fall into the
host ($\mu\approx-1$, $D_{\rm off}>0.6$) should not present a
detectable DM-baryon displacement.

We clearly expect such displacement in the case where the
sub-structure has already passed through the center of the host
halo. In this section we attempt an estimation for the DM-baryon
displacement statistics. We work under the following
hypothesis. First, we consider that systems with $|\mu|<0.9$ have a
baryonic displacement, $d_{2D}^{\rm bar}$, equal to zero. Second, we
consider that all systems with infalling velocities $\mu<-0.9$ and
large displacements $D_{\rm off}>0.6$ also have baryonic displacements
equal to zero. Third, for all the other cases we estimate the
displacement between the baryons and the dominand DM peak by the
distances between the dominant peak and the center of mass of the main
halo, $d_{2D}^{\rm bar}=D_{\rm off} R_{\rm vir}$, where $X_{\rm off}$
is the offset computed for each host halo in the original catalog.

This simplified modeldoes not take into account that there is a
fraction of halos with $\mu<-0.9$ and $D_{\rm off}<0.6$ for which the
collision has not started and should have $d_{2D}^{\rm bar}=0$. A detailed
modeling of this fraction requires the study of the complete merger
tree of the halo and sub-halo, a study beyond the scope of this
Letter. Instead we cautio the reader that the derived fraction of
halos with a displacement $<d_{2D}^{\rm bar}$ can be considered as an
upper limit.

>>>>

The first region has $\mu\approx-1$ and $D_{\rm off}>0.6$, which
locates the systems where a head-on collision has just started. The
sub-halo is close to the boundary of the host halo and is
infalling. The second region has $\mu\approx 1$ and $D_{\rm off}<0.6$;
at this stage the collision continues after the first crossing of the
host's center, the low number of halos with radial infalling velocities
and displacements $D_{\rm off}>0.6$ suggest that this the maximum
range of radii for the apogee.  The third region corresponds to
$\mu\approx-1$ and $D_{\rm off}<0.6$ which corresponds to the
secondary infall after apogee.

@@

These different collision geometries will produce different results in
terms of the displacement between dark matter and baryons. Strictly
speaking, the results we have derived so far, apply to multimodal groups and their
expected separation between the two dominant dark matter clumps but it
should not be interpreted that all have a corresponding DM-baryon
displacement. The systems where the halo is starting to fall into the
host ($\mu\approx-1$, $D_{\rm off}>0.6$) should not present a
detectable DM-baryon displacement.

We clearly expect such displacement in the case where the
sub-structure has already passed through the center of the host
halo. In this section we attempt an estimation for the DM-baryon
displacement statistics. We work under the following
hypothesis. First, we consider that systems with $|\mu|<0.9$ have a
baryonic displacement, $d_{2D}^{\rm bar}$, equal to zero. Second, we
consider that all systems with infalling velocities $\mu<-0.9$ and
large displacements $D_{\rm off}>0.6$ also have baryonic displacements
equal to zero. Third, for all the other cases we estimate the
displacement between the baryons and the dominant DM peak by the
distances between the dominant peak and the center of mass of the main
halo, $d_{2D}^{\rm bar}=D_{\rm off} R_{\rm vir}$, where $X_{\rm off}$
is the offset computed for each host halo in the original catalog.

This simplified model does not take into account that there is a
fraction of halos with $\mu<-0.9$ and $D_{\rm off}<0.6$ for which the
collision has not started and should have $d_{2D}^{\rm bar}=0$. A detailed
modeling of this fraction requires the study of the complete merger
tree of the halo and sub-halo, a study beyond the scope of this
Letter. Instead we caution the reader that the derived fraction of
halos with a displacement $<d_{2D}^{\rm bar}$ can be considered as an
upper limit.
